%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rishi Shah 
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
% \newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
% \newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\newcommand\company{Global Credit Union}
\newcommand\position{IAM Security Analyst}
% \newcommand\location{Chicago, Illinois}


\begin{document}
Brandon Thompson\\
736 Cambridge Way\\
Lake Wales, FL 33853\\
thompson.brandon908@gmail.com\\
(386)466-6700\\


Hiring Manager\\
% \postition{} Security Team\\
%Las Vegas Field Office\\
% Los Gatos, CA 95032\\
% \location{}\\

Dear Hiring Manager

I am writing to express my interest in the \position{} position at the \company{}.
With a solid foundation in cybersecurity and a track record of serving as the sole Security Analyst in my past two positions, I am excited about the opportunity to contribute and develop my skills in a team environment for the \company{}.

My journey into the world of cybersecurity began during my college years, where I discovered my passion for dissecting technology and understanding how it operates.
This intrigue stemmed from my involvement in a FIRST robotics team during high school, where I gained experience working with electronics and coding.
As I pursued my education at Florida Polytechnic University, the diverse topics within the cybersecurity concentration piqued my interest.
I was driven by the desire to demystify the inner workings of the technology we use daily, much like my childhood fascination with disassembling electronic devices.

In my previous role as an Algorithm Developer at Manifold Analytics, the company took on a contract that required the company's network to comply with NIST SP 800-171 requirements.
Recognizing the opportunity to leverage my cybersecurity knowledge, I volunteered to lead the implementation of Security Technical Implementation Guides (STIGs) and audit the devices and network for compliance with NIST standards.
This initiative enabled Manifold Analytics to pursue contracts with esteemed entities such as SOCOM and various government organizations.
My dedication to continuous learning led me to obtain the Certified Ethical Hacker (CEH) certification shortly after completing my degree, while employeed at Manifold Analytics.

In my last two positions, I served as the solo Security Analyst, a role that demanded a diverse skill set, resourcefulness, and the ability to adapt to evolving government requirements and evolving threats and technologies.
This experience honed by ability to work independently and make critical decisions to ensure the security and integrity of organization systems and data.

I am committed to further enhancing my skill set by obtaining additional certification and embracing more technical roles.
A \position{} position at \company{} aligns perfectly with my aspirations and offers an environment that promotes continuous growth, diversity of work, and the opportunity to collaborate with talented individuals.
I am enthusiastic about the prospect of joining the \company{} security team and contributing my expertise to safeguard your systems and data.

I would welcome the opportunity to discuss my qualifications in more detail and elaborate on how I can bring value to \company{}.
Thank you for considering my application.
I look forward to the possibility of meeting with you to explore how I can be a valuable asset to \company{}. 

Sincerely,\\
Brandon Thompson
\end{document}
